---
title: "Sensitivity Analysis"
author: "Jithin Sam Varghese"
date: "January 2, 2019"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###0. Setup
Reading packages
```{r}
library(readxl)
library(ggplot2)
library(data.table)
library(Hmisc)
library(dplyr)
library(tidyr)
library(stringr)
library(binom)
library(gridExtra)
library(grid)
```

Creating file paths
```{r}

if(Sys.info()["user"]=="JVARGH7"){
  path_ic_documentation <- "C:/code/support/interstitial_cystitis/documentation"
  path_ic_data <- "C:/Cloud/OneDrive - Emory University/Papers/Interstitial Cystitis/data"
  path_ic_save <- "C:/Cloud/OneDrive - Emory University/Papers/Interstitial Cystitis/working"
}



```

###1. Data Cleaning
Reading the data into R
```{r}
ic_sensitivity <- readxl::read_xlsx(paste0(path_ic_data,"/De-identified covariates data_20190102.xlsx"))

```


```{r}
colnames(ic_sensitivity) <- c("id","ic_list","cases",
                  "age_last_visit","gender","race","smoking",
                  "elmiron","hydroxyzine","tca","gabapentin","hydroxychloroquine",
                  "cyclobenzaprine","methenamine","phenazopyridine","oxybutynin")
ic_sensitivity <-  ic_sensitivity %>% filter(!is.na(id))
```

```{r}
ic_sensitivity <- ic_sensitivity %>% filter(!is.na(ic_list))
```


Labeling different columns
```{r}
ic_sensitivity$cases <- as.factor(ic_sensitivity$cases)
levels(ic_sensitivity$cases) <- c("1 Definite","2 Possibly", "3 Not", "4 No images")
table(ic_sensitivity$cases,useNA = "always")

```

```{r}
ic_sensitivity$gender <- as.factor(ic_sensitivity$gender)
levels(ic_sensitivity$gender) <- c("1 Female", "2 Male")
table(ic_sensitivity$gender, useNA= "always")
```

```{r}
ic_sensitivity$race <- as.factor(ic_sensitivity$race)
levels(ic_sensitivity$race) <- c("1 White","2 Black", "3 Other")
table(ic_sensitivity$race,useNA = "always")
```

```{r}
ic_sensitivity$smoking <- as.factor(ic_sensitivity$smoking)
levels(ic_sensitivity$smoking) <- c("1 Never", "2 Current", "3 Former")
table(ic_sensitivity$smoking,useNA = "always")
```

```{r}
ic_sensitivity$elmiron <- with(ic_sensitivity,ifelse(!is.na(elmiron),1,0))
ic_sensitivity$hydroxyzine <- with(ic_sensitivity,ifelse(!is.na(hydroxyzine),1,0))
ic_sensitivity$tca <- with(ic_sensitivity,ifelse(!is.na(tca),1,0))
ic_sensitivity$gabapentin <- with(ic_sensitivity,ifelse(!is.na(gabapentin),1,0))
ic_sensitivity$hydroxychloroquine <- with(ic_sensitivity,ifelse(!is.na(hydroxychloroquine),1,0))
ic_sensitivity$cyclobenzaprine <- with(ic_sensitivity,ifelse(!is.na(cyclobenzaprine),1,0))
ic_sensitivity$methenamine <- with(ic_sensitivity,ifelse(!is.na(methenamine),1,0))
ic_sensitivity$phenazopyridine <- with(ic_sensitivity,ifelse(!is.na(phenazopyridine),1,0))
ic_sensitivity$oxybutynin <- with(ic_sensitivity,ifelse(!is.na(oxybutynin),1,0))

ic_sensitivity <- ic_sensitivity %>% mutate_at(c("elmiron","hydroxyzine",
                         "tca","gabapentin","hydroxychloroquine",
                         "cyclobenzaprine","methenamine",
                         "phenazopyridine","oxybutynin"),
                       funs(factor(.,labels=c("no","yes"))))
```

Generating Summary Statistics:
The variable ID has been ignored.
```{r}
describe(ic_sensitivity %>% select(-id,-ic_list))
```

###2. 1,2 vs 3,4
####A. Hypothesis Tests

```{r}
ic_sensitivity$outcome <- with(ic_sensitivity, as.factor(ifelse(cases %in% c("1 Definite", "2 Possibly"),"yes","no")))
table(ic_sensitivity$outcome,useNA="always")
```

#####Summary for Cases (Outcome = Yes)
```{r}
describe(ic_sensitivity %>% filter(outcome=="yes") %>% select(-id,-ic_list))
```

#####Summary for Non-cases (Outcome = No)
```{r}
describe(ic_sensitivity %>% filter(outcome=="no") %>% select(-id,-ic_list))
```

#####Fisher's Exact Tests
Odds ratio values given here are "hypothesized odds ratio"- different from sample odds ratio which we typically report.
Sample odds ratio given in next section
```{r}
ic_sensitivity %>% select(-id,-ic_list,-cases,-outcome,-age_last_visit) %>% 
  sapply(.,y= ic_sensitivity$outcome,function(x,y) fisher.test(y,x))
```

Levene's test for Equality of variance does not reject the null hypothesis (Variances are equal)
```{r}
car::leveneTest(age_last_visit~outcome,data=ic_sensitivity)
```
We will use Independent Two-sample T-test (Pooled)
We do not reject the null hypothesis that age at last visit is different across the outcome group
```{r}
t.test(age_last_visit~outcome,data=ic_sensitivity,var.equal=TRUE)
```


```{r}
with(ic_sensitivity,table(outcome,elmiron))
```
#####Sample Odds ratio
```{r}
ic_sensitivity %>% select(-id,-ic_list,-cases,-outcome,-age_last_visit) %>% 
  sapply(.,y= ic_sensitivity$outcome,function(x,y) exp(coef(glm(y~x,family="binomial"))))
```

```{r}
confint_glm <- function(x,y){
  mod <- glm(y~x,family="binomial")
  mod_df <- broom::tidy(mod)
  mod_df <- mod_df %>% mutate(lci = exp(estimate-1.96*std.error),
                              uci = exp(estimate+1.96*std.error)) %>% 
    mutate(estimate = exp(estimate)) %>% select(term,estimate,lci,uci)
  print(mod_df)
}


ic_sensitivity %>% select(-id,-cases,-outcome,-ic_list) %>% 
  sapply(.,y= ic_sensitivity$outcome,function(x,y) {confint_glm(x,y)})

```

