---
title: "1. Exploratory Analysis"
output:
  pdf_document: default
  html_document: default
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###0. Setup
Reading packages
```{r}
library(tidyverse)
```

Creating file paths
```{r}

if(Sys.info()["user"]=="JVARGH7"){
  path_ic_documentation <- "C:/code/support/interstitial_cystitis/documentation"
  path_ic_data <- "C:/Cloud/OneDrive - Emory University/Papers/Interstitial Cystitis/data"
  path_ic_save <- "C:/Cloud/OneDrive - Emory University/Papers/Interstitial Cystitis/working"
}



```

IC- Billing
EMA IC- Medical Record
x - Yes

###1. Data Cleaning
Reading the data into R
```{r}
ic <- readxl::read_xlsx(paste0(path_ic_data,"/De-identified covariates data_20190111.xlsx"))

```

Renaming columns:
The column names were changed to make it suitable for analysis
```{r}
colnames(ic) <- c("id","ic_list","ema_ic_dx_search","ic_chart_review","ic_diagnosis","cases",
                  "age_last_visit","gender","race","smoking",
                  "elmiron","hydroxyzine","tca","gabapentin","hydroxychloroquine",
                  "cyclobenzaprine","methenamine","phenazopyridine","oxybutynin")
ic <- ic[!is.na(ic$id),]
```

Creating dataset
```{r}
ic <- ic %>% 
  filter(ic$ic_diagnosis == "1")
```

```{r}
ic <- ic %>% 
  mutate(source_billing = case_when(ic_list == "x"~ "yes",
                             TRUE ~ "no"),
         source_records = case_when(ema_ic_dx_search == "x" ~ "yes",
                                    TRUE ~ "no")) %>% 
  select(id,source_billing,source_records,
         cases:oxybutynin) 
```


Labeling different columns
```{r}
ic$cases <- as.factor(ic$cases)
levels(ic$cases) <- c("1 Definite","2 Possibly", "3 Not", "4 No images")
table(ic$cases,useNA = "always")

```

```{r}
ic$gender <- as.factor(ic$gender)
levels(ic$gender) <- c("1 Female", "2 Male")
table(ic$gender, useNA= "always")
```


```{r}
ic$race <- as.factor(ic$race)
levels(ic$race) <- c("1 White","2 Black", "3 Other")
table(ic$race,useNA = "always")
```

```{r}
ic <- ic %>% 
  mutate(smoking = case_when(smoking == "1"~ "1 Never",
                             smoking == "2" ~ "2 Current",
                             smoking == "3" ~ "3 Former",
                             TRUE ~ "Missing")) %>% 
  mutate(smoking = as.factor(smoking))

table(ic$smoking)

```

```{r}
ic$elmiron <- with(ic,ifelse(!is.na(elmiron),1,0))
ic$hydroxyzine <- with(ic,ifelse(!is.na(hydroxyzine),1,0))
ic$tca <- with(ic,ifelse(!is.na(tca),1,0))
ic$gabapentin <- with(ic,ifelse(!is.na(gabapentin),1,0))
ic$hydroxychloroquine <- with(ic,ifelse(!is.na(hydroxychloroquine),1,0))
ic$cyclobenzaprine <- with(ic,ifelse(!is.na(cyclobenzaprine),1,0))
ic$methenamine <- with(ic,ifelse(!is.na(methenamine),1,0))
ic$phenazopyridine <- with(ic,ifelse(!is.na(phenazopyridine),1,0))
ic$oxybutynin <- with(ic,ifelse(!is.na(oxybutynin),1,0))

ic <- ic %>% mutate_at(c("elmiron","hydroxyzine",
                         "tca","gabapentin","hydroxychloroquine",
                         "cyclobenzaprine","methenamine",
                         "phenazopyridine","oxybutynin"),
                       funs(factor(.,labels=c("no","yes"))))
```

```{r}
ic$outcome <- with(ic, as.factor(ifelse(cases %in% c("1 Definite", "2 Possibly"),"yes","no")))

ic <- ic %>% 
  mutate(outcome = case_when(cases %in% c("1 Definite", "2 Possibly") ~ "yes",
                             TRUE ~ "no")) %>% 
  mutate(outcome = as.factor(outcome))

table(ic$outcome,useNA="always")
```

Generating Summary Statistics:
The variable ID has been ignored.
```{r}
library(tableone)

vars_table1 <- ic %>% 
  select(-id) %>% 
 names()
tab1 <- tableone::CreateTableOne(c(vars_table1),data=ic, includeNA = TRUE) %>% 
  print(exact = "stage", quote = FALSE, noSpaces = TRUE, printToggle = FALSE)
print(tab1)
write.csv(tab1, paste0(path_ic_save,"/tableone_overall.csv"))
```

```{r}
Hmisc::describe(ic %>% filter(outcome == "yes") %>% select(-id,-outcome))
```


```{r}
Hmisc::describe(ic %>% filter(outcome == "no") %>% select(-id,-outcome))
```


###2. 1,2 vs 3,4
####A. Hypothesis Tests



```{r}
vars_table1 <- ic %>% 
  select(-id,-cases) %>% 
 names()
tab1_2 <- tableone::CreateTableOne(c(vars_table1), strata="outcome",data=ic,includeNA = TRUE) %>% 
  print(exact = "stage", quote = FALSE, noSpaces = TRUE, printToggle = FALSE)
print(tab1_2)
write.csv(tab1_2, paste0(path_ic_save,"/tableone_stratified.csv"))
```


```{r}

```


#####Fisher's Exact Tests
Odds ratio values given here are "hypothesized odds ratio"- different from sample odds ratio which we typically report.
Sample odds ratio given in next section
```{r}
ic_fishers <- ic %>% select(-id,-cases,-source_billing,-source_records,-outcome,-age_last_visit) %>% 
  sapply(.,y= ic$outcome,function(x,y) fisher.test(y,x))
```

```{r}
t.test(age_last_visit~outcome,data=ic,var.equal=TRUE)
age_p <- t.test(age_last_visit~outcome,var.equal=TRUE,data=ic)$p.value
```


```{r}
fishers_df <- bind_rows(t(map_df(ic_fishers,~.x$p.value)) %>% 
                          data.frame() %>%
                          setNames("p_test") %>% 
                          mutate(var = rownames(.)),
                        data.frame(p_test = age_p, var = "age_last_visit")
) %>% 
  arrange(p_test) %>% 
  mutate(rank = seq(1:nrow(.))) %>% 
  mutate(hb_cutoff = 0.05/(nrow(.)-rank+1)) %>% 
  mutate(significance = case_when(p_test < hb_cutoff ~ "yes",
                                  TRUE ~ "no")) %>% 
  mutate(p_value = round(p_test,3))
write.csv(fishers_df, paste0(path_ic_save,"/tableone_fishers.csv"))
print(fishers_df)
```


#####Sample Odds ratio
```{r}
ic_sor <- ic %>% select(-id,-cases,-source_billing,-source_records,-outcome,-age_last_visit) %>% 
  sapply(.,y= ic$outcome,function(x,y) exp(coef(glm(y~x,family="binomial"))))


tidy_estimates <- function(x,y){
  broom::tidy(x) %>% 
    mutate(var = y)
}

ic_glm <- ic %>% select(-id,-cases,-source_billing,-source_records,-outcome) %>% 
  lapply(.,y= ic$outcome,function(x,y) glm(y~x,family="binomial"))

tidy_coefficients <- map2_df(ic_glm,names(ic_glm),function(x,y) {tidy_estimates(x,y)}) %>% 
  mutate(exp_estimate = case_when(str_detect(term,"sd_") ~ estimate,
                              TRUE ~ exp(estimate)),
         exp_lci = case_when(str_detect(term,"sd_") ~ NA_real_,
                              TRUE ~ exp(estimate -1.96*std.error)),
         exp_uci = case_when(str_detect(term,"sd_") ~ NA_real_,
                              TRUE ~ exp(estimate +1.96*std.error))) %>% 
  mutate(odds_ratio = paste0(round(exp_estimate,2),
                             " (",round(exp_lci,2),
                             ",",round(exp_uci,2),
                             ")"))
write.csv(tidy_coefficients, paste0(path_ic_save,"/tableone_sor.csv"))
```

###3. Stratify by Elmiron status
```{r}

vars_table2 <- ic %>% 
  select(cases,outcome) %>% 
 names()
tab2 <- tableone::CreateTableOne(c(vars_table2), strata="elmiron",data=ic) %>% 
  print(exact = "stage", quote = FALSE, noSpaces = TRUE, printToggle = FALSE)
print(tab2)
write.csv(tab2, paste0(path_ic_save,"/tabletwo_elmiron.csv"))

```


```{r}
tab2 <- tableone::CreateTableOne(c(vars_table2),data=ic) %>% 
  print(exact = "stage", quote = FALSE, noSpaces = TRUE, printToggle = FALSE)
print(tab2)
```


###4. Save
```{r}
saveRDS(ic,paste0(path_ic_save,"/ic_submit.RDS"))
```

